---
title: "Homework 2"
author: "Key"
format: pdf
execute:
  error: false
  message: false
  warning: false
---

```{r setup}
#| label: setup
#| include: false

library(nlme)
library(janitor)
library(tidyverse)
```

1.  Install the `{nlme}` package

2.  Load `{nlme}`, `{janitor}`, and the `{tidyverse}` packages in the "setup" chunk

3.  Run the chunk below to prep some data from the `{nmle}` package for plotting

```{r}
#| label: data
#| echo: true

pd <- Oxboys %>% 
  clean_names() %>% 
  mutate(subject = factor(subject),
         occasion = factor(occasion)) %>% 
  filter(subject == "10" | subject == "4" | subject == "7") %>% 
  as_tibble()
```

\newpage

4.  Reproduce the following two plots, using the *pd* data. You can use whatever theme you want (I used `theme_minimal()`), but all else should be the same.

```{r}
#| label: plots1

theme_set(theme_minimal())

# Put code below for Plot 1. Note that Plot 1 is a line plot, not a "smooth."

ggplot(pd, aes(age, height)) +
  geom_line() +
  facet_wrap(~subject) +
  labs(title = "Plot 1")

# Put code below for Plot 2. Note that Plot 2 is a line plot also.

ggplot(pd, aes(age, height, color = subject)) +
  geom_line() +
  labs(title = "Plot 2")
```

\newpage

5.  Use the *mtcars* dataset from base `R` to replicate the following plots. (Just type *mtcars* into the console to see the dataset).

```{r}
#| label: plots2

# Put code below for Plot 3
ggplot(mtcars, aes(drat, mpg)) +
  geom_point() +
  labs(title = "Plot 3")

# Put code below for Plot 4
ggplot(mtcars, aes(drat, mpg)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Plot 4")

# Put code below for Plot 5
ggplot(mtcars, aes(drat, mpg)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~vs) +
  labs(title = "Plot 5")

# Put code below for Plot 6. I have given you the first line of code to start.
ggplot(mtcars, aes(drat, mpg, color = factor(cyl))) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Plot 6")

```

\newpage

6.  Use the *Orange* dataset, also part of base `R`, to replicate the following plots.

```{r}
#| label: orange-plots

# Put code below for Plot 7
ggplot(Orange, aes(age, circumference, color = Tree)) +
  geom_line() +
  geom_point() +
  labs(title = "Plot 7")


# Put code below for the last plot. See slide xx from the w3 class for labels.
ggplot(Orange, aes(age, circumference)) +
  geom_smooth(method = "lm", se = FALSE, color = "gray40") +
  geom_point(aes(color = Tree), size = 3) +
  labs(x = "Age of the Tree (in days)",
       y = "Circumference of the Trunk (in mm)",
       title = "Orange Tree Growth",
       subtitle = "Gray line displays a linear model fit to the data.")


```
