---
title: "Homework 3"
author: "Your Name Here"
format: html
execute: 
  error: true
  message: false
  warning: false
---

```{r}
#| label: packages
#| include: false

library(tidyverse)
library(ggridges)
library(ISLR)
```

1.  Load the `{tidyverse}`, `{ggridges}`, and `{ISLR}` packages in the "setup" chunk. (Install any if needed.)

2.  Run the following lines of code to read about and view the data we'll use for this lab.

-   Comment out line 32 after you run it, but putting a `#` at the start of the line.

```{r}
#| label: gsscat
#| eval: false

str(gss_cat)
View(gss_cat)
?gss_cat
```

3.  Use `{ggplot2}` to create a histogram of `tvhours`. The plot should:

-   Include a small amount of transparency so grid lines are visible under the histogram.
-   Be a different color than the default
-   Include meaningful axis labels
-   Have a title and a subtitle

```{r}
#| label: question-3

theme_set(theme_minimal())

ggplot(gss_cat, aes(tvhours)) +
  geom_histogram(fill = "cornflowerblue", 
                 alpha = 0.7) +
  labs(x = "Number of Hours Watching Television",
       y = "Number of Observations",
       title = "Distribution of Television Watching",
       subtitle = "Data from the General Social Survey (http://gss.norc.org)")
```

4.  Create a ridgeline density plot of `age` by `partyid`. Do you notice any strong differences by party affiliation?

```{r}
#| label: question-4

ggplot(gss_cat, aes(age, partyid)) +
  geom_density_ridges(fill = "cornflowerblue", alpha = 0.4)
```

5.  Modify the plot from Question 4 to produce separate ridgeline densities by `race` within one plot. Do you see any patterns?

```{r}
#| label: question-5

ggplot(gss_cat, aes(age, partyid)) +
  geom_density_ridges(aes(fill = race), alpha = 0.4)
```

6.  Replicate the plots from Questions 4 and 5, but this time displaying the relations with boxplots (i.e., one boxplot from Question 4 and one boxplot for Question 5 in the chunk below). Try using `coord_flip`. Which do you think displays the relation more clearly? Why?

```{r}
#| label: boxplots

ggplot(gss_cat, aes(partyid, age)) +
  geom_boxplot(fill = "cornflowerblue") +
  coord_flip()

ggplot(gss_cat, aes(partyid, age)) +
  geom_boxplot(aes(fill = race), alpha = 0.4) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

7.  Run the following lines of code to get a correlation table as a data frame.

```{r}
#| label: corr-mat-df

cor_tbl <- Hitters %>% 
  select_if(is.numeric) %>% 
  cor(use = "pairwise.complete.obs") %>% 
  as.data.frame() %>% 
  mutate(row = row.names(.)) %>% 
  gather(col, cor, -row) %>% 
  tbl_df()
```

Use the correlation table to create a heatmap using `geom_tile`. Change the colors to one of the four `viridis` palettes. What does the heatmap help you see?

```{r}
#| label: heatmap

ggplot(cor_tbl, aes(row, col, fill = cor)) +
  geom_tile() +
  scale_fill_viridis_c(option = "inferno") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


